### 2014-03-14 src/analysis.Rnw
update

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criteria, we computed the
correlation between sampled mutation score and full mutation score.
Since for most of the sampling criteria, if there are no mutants to
sample, it probably means there are no mutants generated on the whole,
we used $lm(M_{all}~0+M_{sample})$ as the regression formula, and report
the correlation from this linear regression. We also report the expected
multiplier factor for the sampled mutation score. This factor determines
the ease of satisfying the sampling criteria. That is, if the multiplier
factor is small, then it is easier to satisfy compared to a larger multiplier
factor.
Next, for each criteria, we computed the reduction of mutants given by the
ratio between total number of mutants and sampled mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. (A large amount of standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. So as a heuristic, we suggest looking at only those projects which
has a mean reduction ratio at least twice the standard deviation.)

For some of the smaller projects, some of the sampling criteria did not
return any results. This is also collected in our tables.

>>>>

\section{Analysis}
\label{sec:analysis}
For the purposes of comparing between the criteria, we computed the
correlation between sampled mutation score and full mutation score.
Since for most of the sampling criteria, if there are no mutants to
sample, it probably means there are no mutants generated on the whole,
we used
\[\mu_\{M_{all}|M_{reduced}\} = 0 + \beta_1 \times M_{reduced}\]
as the regression formula, and report
the correlation from this linear regression. We also report the expected
multiplier factor $\beta_1$ for the sampled mutation score. This factor
determines the ease of satisfying the sampling criteria. That is, if the
multiplier factor is small, then it is easier to satisfy compared to a
larger multiplier factor.

Next, for each criteria, we computed the reduction of mutants given by the
ratio between total number of mutants and sampled mutants.
We also compute standard deviation of the mutant reduction, which determines
the consistency of results. (A large amount of standard deviation suggests
that the mutant reduction ratio achieved is very much dependent on the
project. So as a heuristic, we suggest looking at only those projects which
has a mean reduction ratio at least twice the standard deviation.)

A few projects did not return any results for some large reduction factors.
This number of valid results from projects are also collected in the result
tables.
